Clean data

### 2019-06-22 analysis/02_clean-data.Rmd
Add raw and clean data

```{r clean-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(donorheuristics)
library(here)

col_names <- names(read_csv(here::here("data", "conjointqsf_final.csv")))
data <- read_csv(
  here::here("data", "conjointqsf_final.csv"),
  skip = 2,
  col_names = col_names
)
```

@@

```{r clean-data, warning=FALSE, message=FALSE}
data %>%
  summarize(
    total = n(),
    finished = sum(V10)
  )
```

@@

```{r clean-data, warning=FALSE, message=FALSE}
data %>%
  count(Q1.1)

@@

```{r clean-data, warning=FALSE, message=FALSE}
data %>%
  count(Q2.5)

@@

```{r clean-data, warning=FALSE, message=FALSE}
data %>%
  count(Q2.9)

@@

```{r clean-data, warning=FALSE, message=FALSE}
data %>%
  count(Q2.11)
```

@@

```{r clean-data, warning=FALSE, message=FALSE}
data %>%
  count(Q5.17)
```

@@

```{r clean-data, warning=FALSE, message=FALSE}
data_clean <- data %>%
  filter(V10 == 1) %>%         # Keep respondents who completed the entire survey
  filter(Q1.1 == 1) %>%        # Keep respondents who gave consent
  filter(Q2.5 %in% c(1:5)) %>% # Keep respondents who passed the screener
  filter(Q2.11 == 3)           # Keep respondents who passed the attention check
```

@@

```{r clean-data, warning=FALSE, message=FALSE}
# Finished respondents
data_clean %>% 
  summarize(
    total = n(),
    finished = sum(V10)
  )

@@

```{r clean-data, warning=FALSE, message=FALSE}
data_clean %>%
  count(vers_CBCONJOINT) %>%
  count(n)
```

@@

```{r clean-data, warning=FALSE, message=FALSE}
data_clean %>%
  select(Q4.1:Q4.12) %>%
  gather(key = "task", value = "choice") %>%
  count(choice)
```

@@

```{r clean-data, warning=FALSE, message=FALSE}
design_orig <- read_csv(here("data", "design.csv")) %>% 
  rename(
    version = question_set,
    task = question,
    alt = choice
  ) %>% 
  gather(key = "atts", value = "levels", -c(version:alt))

@@

@@

```{r clean-data, warning=FALSE, message=FALSE}
data <- data_clean

write_csv(data, here("data", "final_data.csv"))
```

>>>>

We downloaded the `conjointqsf_final.csv` file directly from Qualtrics and ran this code to remove identifying information. We then saved that CSV file as `conjointqsf_final.csv` and include it in `data/raw_data` for distribution. We use the de-identified file in the rest of our data cleaning and analysis.

```r
library(tidyverse)
library(donorheuristics)
library(here)

col_names <- names(read_csv(here::here("data", "private_data", "conjointqsf_final.csv")))
data <- read_csv(
  here::here("data", "private_data", "conjointqsf_final.csv"),
  skip = 3,
  col_names = col_names,
  guess_max = 1500
)

# Remove IP address and location information
data %>% 
  select(-V6, -LocationLatitude, -LocationLongitude, -LocationAccuracy) %>% 
  write_csv(here::here("data", "raw_data", "conjointqsf_final.csv"))
```

```{r load-raw-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(donorheuristics)
library(here)

data <- read_csv(
  here::here("data", "raw_data", "conjointqsf_final.csv"),
  guess_max = 1500
)
```

@@

```{r number-finished}
data %>%
  summarize(
    total = n(),
    finished = sum(V10)
  )
```

@@

```{r consent}
data %>%
  count(Q1.1)

@@

```{r screening}
data %>%
  count(Q2.5)

@@

```{r display-logic}
data %>%
  count(Q2.9)

@@

```{r attention-check}
data %>%
  count(Q2.11)
```

@@

```{r confirm-ages}
data %>%
  count(Q5.17)
```

@@

```{r clean-data}
data_clean <- data %>%
  filter(V10 == 1) %>%         # Keep respondents who completed the entire survey
  filter(Q1.1 == 1) %>%        # Keep respondents who gave consent
  filter(Q2.5 %in% c(1:5)) %>% # Keep respondents who passed the screener
  filter(Q2.11 == 3)           # Keep respondents who passed the attention check
```

@@

```{r clean-data-confirmation}
# Finished respondents
data_clean %>% 
  summarize(
    total = n(),
    finished = sum(V10)
  )

@@

```{r choice-clean}
data_clean %>%
  count(vers_CBCONJOINT) %>%
  count(n)
```

@@

```{r design-random-assignment}
data_clean %>%
  select(Q4.1:Q4.12) %>%
  gather(key = "task", value = "choice") %>%
  count(choice)
```

@@

```{r check-design, warning=FALSE, message=FALSE}
design_orig <- read_csv(here("data", "derived_data", "design.csv")) %>% 
  rename(
    version = question_set,
    task = question,
    alt = choice
  ) %>% 
  gather(key = "atts", value = "levels", -c(version:alt))

@@

## Remove extraneous information

```{r shrink-data}
data <- data_clean %>% 
  mutate(id = row_number()) %>% 
  rename(version = vers_CBCONJOINT) %>% 
  select(id, version, Q1.1:Q5.18)
```

@@

```{r save-clean-data}
write_csv(data, here("data", "derived_data", "final_data.csv"))
```
